Opportunities for improvement in the care of adult trauma patients arriving

### 2025-05-30 manuscript.Rmd
testar knitta från ny dator

---
title: Opportunities for improvement in the care of adult trauma patients arriving
  in shock
author: "Carl Skog"
output:
  word_document: default
  #bookdown::pdf_document2:
    #latex_engine: xelatex
  #html_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

>>>>

---
title: Opportunities for improvement in the care of adult trauma patients arriving
  in shock
author: "Carl Skog"
output:
  #word_document: default
  #bookdown::pdf_document2:
    #latex_engine: xelatex
  html_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---
